### 2012-09-07 joint action and knowing others minds/conf budapest ceu talk cognitive 2012-09/interacting mindreaders HANDOUT.tex
moved folders

\begin{center}
{
\textbf{Joint Action and the Emergence of Mindreading}
\Large{Interacting Mindreaders}
}

@@

<s.butterfill@warwick.ac.uk>

@@

Could an interacting mindreader be in a position to know things which she would be unable to know were she unable to interact with her targets?

@@

%(Cf.\ Southgate et al's principle of efficiency:
%`goal attribution requires that agents expend the least possible amount of energy within their motor constraints to achieve a certain end.' \citep%[p.\ 1061]
%{Southgate:2008el})

@@

`the adult’s social cues conveyed her communicative intent, which in turn encouraged the child to `see through the sign'.'
\citep%[p.\ 118]
{leekam_adults_2010}

>>>>

\begin{center}
{
\Large{Interacting Mindreaders}
}

@@

<butterfillS@ceu.hu>

@@

Could interacting mindreaders be in a position to know things which they would be unable to know if they were manifestly passive observers?

\section{Terminology}
\emph{Mindreading}: `In saying that an individual has a theory of mind, we mean that the individual imputes mental states to himself and to others ... the system can be used to make predictions, specifically about ... behavior.'\citep{premack_does_1978} %(Premack & Woodruff 1978: 515)

\emph{Sophisticated forms of mindreading} involve imputing propositional attitudes such as belief, desire and intention in the course of constructing or evaluating  reason-giving, causal explanations of action.

%\section{Joint action}
%Paradigm cases in philosophy include two people 
%	painting a house together, \citep{Bratman:1992mi}
%	lifting a heavy sofa together, \citep{Velleman:1997oo} 
%	preparing a hollandaise sauce together, \citep{Searle:1990em}
%	going to Chicago together, \citep{Kutz:2000si} 
%	and walking together. \citep{gilbert_walking_1990}
%
%In developmental psychology paradigm cases of joint action include  two people 
%	tidying up the toys together, \citep{Behne:2005qh}
%	cooperatively pulling handles in sequence to make a dog-puppet sing, \citep{Brownell:2006gu} 
%	and bouncing a block on a large trampoline together.\citep{Tomasello:2007gl}
%
%Other paradigm cases from research in cognitive psychology include two people
%	lifting a two-handled basket,  \citep{Knoblich:2008hy}
%	putting a stick through a ring, \citep{ramenzoni_joint_2011}
%	and swinging their legs in phase.\citep%[p. 284]
%	{schmidt_richardons:_2008}

\section{The Problem of Opaque Means}
Ignorance about to which ends actions are means can be an obstacle to goal ascription.

\section{Distributive Goals}
A \emph{goal} is an outcome to which actions are, or might be, directed.  A \emph{goal-state} is an intention or other state of an agent linking an action to a goal to which it is directed.

%A \emph{goal-directed joint action} is a joint action which, taken as a whole, is directed to a goal.

The \emph{distributive goal} of two or more actions is G: (a) each action is individually directed to G; and (b) it is possible that: all actions succeed relative to this outcome.

%\textbf{Collective goal}.  The \emph{collective goal} of two or more actions is G:
%(a) G is a distributive goal of the outcomes;
%(b) the actions are coordinated; and 
%(c) coordination of this type would normally  facilitate occurrences of outcomes of G's type

@@

(Contrast a principle of efficiency:
`goal attribution requires that agents expend the least possible amount of energy within their motor constraints to achieve a certain end.' \citep%[p.\ 1061]
{Southgate:2008el})

@@

Leekam et al.: `the adult’s social cues conveyed her communicative intent, which in turn encouraged the child to `see through the sign'.'
\citep%[p.\ 118]
{leekam_adults_2010}

Csibra: Early in human development,
teleological and referential action interpretation 
`rely on different kinds of action understanding' %\citep[p.\ 456]{Csibra:2003kp}
and
involve two distinct `action interpretation systems'   %\citep[p.\ 456]{Csibra:2003kp} 
which come together later in development.\citep{Csibra:2003kp}
